Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-19 paper/paper.qmd
Updated mutate days_towards_election

library(tidyverse)
```

@@

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

>>>>

library(tidyverse)
library(skimr)
library(knitr)
```

@@

Telegraphing paragraph: The remainder of this paper is structured as follows.

```{r}
data <- read.csv("../data/01-raw_data/president_polls.csv")
skim(data)

```{r}
colnames(data)
```

pollster

pollscore, numeric_grade

sponsor_candidate, sponsor_candidate_party

sample_size

```{r}
unique(data$election_date)
```

```{r mutate days_towards_election}
data <- data %>% 
  select(end_date) %>% 
  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))

# Define the election date
election_date <- as.Date("11/5/24", format="%m/%d/%y")

# Calculate the days towards the election date
data <- data %>% 
  mutate(days_towards_election = as.numeric(difftime(end_date,election_date, units = "days")))
```

```{r}
data_a <- data %>% 
  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))

# Define the election date
election_date <- as.Date("11/5/24", format="%m/%d/%y")

# Calculate the days towards the election date
data_a <- data_a %>% 
  mutate(days_towards_election = as.numeric(difftime(end_date,election_date, units = "days")))
```

# Load necessary libraries
library(GGally)
library(dplyr)

# Select only numerical columns from your dataframe
numeric_data <- data %>% 
  select(where(is.numeric)) %>% 
  select(numeric_grade, pollscore, transparency_score, sample_size, pct) %>% 
  filter(complete.cases(.))

# Create a pair plot
ggpairs(numeric_data)

```{r}
data %>% 
  select(numeric_grade, pollscore) %>% 
  filter(complete.cases(.)) %>% 
  cor()
```

```{r}
sort(unique(data$sample_size)) %>% 
  summary()
```

```{r}
data %>% 
  filter(numeric_grade >= 2.0) %>% 
  skim()
```

```{r}
data %>%
